\documentclass[letterpaper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\setitemize{itemsep=-2pt}
\geometry{margin=0.2in}
\linespread{0}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    }

\begin{document}

% Header
\begin{center}
    \Large{\textbf{Sean Gatewood}}\\[0.5em]
    \normalsize
    Email: \href{mailto:stg2bd@virginia.edu}{stg2bd@virginia.edu} $\vert$ \href{https://linkedin.com/in/sean-t-gatewood}{sean-t-gatewood} $\vert$ \href{https://github.com/sgatewood}{sgatewood}
\end{center}

\vspace{-2.9em}


\newcommand{\heading}[1]
{
    \section*{\textgreater\textgreater \space #1}
    \vspace{-0.9em}
    \rule{\linewidth}{0.4pt}
}

% Education
\heading{Education}
\textbf{University of Virginia} (May 2020), Rodman Scholar, Raven Society
\begin{itemize}
    \item B.S. Computer Science. GPA: 3.95\\
\end{itemize}

\noindent\textbf{Notable Courses}: Computer Graphics, Algorithms, Introduction to Cybersecurity, Software Testing
\vspace{-1em}

% Experience
\newenvironment{job}[3]
{
    \noindent\textbf{#1} (#2) \hfill #3
    \begin{minipage}{0.8\textwidth}
    \begin{itemize}
}
{
    \end{itemize}
    \end{minipage}
}

\heading{Experience}

\begin{job}
{DevOps Engineer, Digital Asset}
{New York, New York / remote}
{April 2023 -- Present}
    \item Develop and maintain infrastructure around critical k8s services.
    \item Automated the entire (from-scratch) deployment of a critical service into its own cluster with all the cloud infrastructure it needed. Utilized GCP, terraform, jsonnet, bash, and helm. Instrumented monitoring/alerts with DataDog as well, and regularly use it to tune our configuration.
    \item Regularly engineered automation to seamlessly navigate complex migrations in production with minimal downtime.
    \item Authored a custom k8s operator in Go to satisfy a particular business need.
    \item Developed CI/CD pipelines using Google Cloud Build and CircleCI.
\end{job}

\begin{job}
{Software Engineer II, Appian Corporation}
{McLean, VA / remote}
{August 2020 -- April 2023}
    \item Member of a scrum team that created and maintained a variety of developer tooling and infrastructure.
    \item Contributed to a remote development solution, including a custom Kubernetes service to lease EC2s and a python tool to build/develop/test the product remotely (rather than on your own machine).
    \item Architected and developed a pipeline to create warm builds that developers can take and use instantly rather than waiting to build from source.
    \item Initiated \& developed numerous prototypes, many of which shipped (or became real quarter-long features for my team).
    \item Regularly initiated \& led architectural design discussions.
    \item Regularly assisted developers in troubleshooting technical issues, both to help unblock them and to find ways to improve our local build stability.
    \item Treasured high code quality standards and contributed to our data-driven goal to lead the department in code quality and component health.
    \item Mentored two interns as a Summer Intern Manager, meeting with them weekly to optimize their internship experience.
\end{job}

\begin{job}
{Software Engineering Intern, Uber Advanced Technologies Group}
{Pittsburgh, PA}
{May 2019 -- August 2019}
    \item Developed and benchmarked alternate implementations for a key-value store using various database technologies (e.g. LevelDB, Sqlite3).
    \item Presented results to Uber ATG software engineers.
\end{job}

\begin{job}
{Teaching Assistant - Introduction to Programming, University of Virginia}
{Charlottesville, VA}
{Fall 2017 -- May 2020}
    \item Assisted hundreds of students with introductory programming concepts in Python.
    \item Created review videos that have received over 13,000 views.
    \item Helped manage the course as one of four "Head TAs."
    \item Saved TA time/effort by automating the grading of a remote google docs exam question using Python.
    \item Worked with many students directly in office hours, encouraging many that they can learn to code.
\end{job}

\begin{job}
{Software Engineering Intern, NASA Langley Research Center}
{Hampton, VA}
{May 2018 -- May 2019}
    \item Data Management for Airborne Atmospheric Composition Data.
    \item Added HDF file compatibility to NASA’s TOLNet File Format Scanner and Curtain/Profiles Plotter.
    \item Engineered a full-stack web application (JQuery, AJAX, cgi, C++) for atmospheric researchers to create customized data merges.
    \item Presented a working prototype to atmospheric researchers and received design feedback.
    \item Continued part-time development during the fall and spring semesters to harden the merge tool.
\end{job}

\vspace{-1em}

% Skills
\heading{Skills (non-comprehensive, in order of proficiency)}
\begin{minipage}{0.8\textwidth}
\begin{itemize}
\item\textbf{Languages:} Python, Bash, Go, Java, JavaScript, C++, Groovy / Kotlin\\
\item\textbf{Other technologies:} Kubernetes, Terraform, Helm, GitLab pipelines, Feature Toggles / LaunchDarkly, Unit testing / mocking, Vim, Git, SQL, Docker, Terraform / AWS, Functional programming
\end{itemize}
\end{minipage}
\vspace{-1em}

% Projects
\newenvironment{project}[2]
{
    \noindent\textbf{#1} \hfill #2\\
    \begin{minipage}{0.8\textwidth}
    \begin{itemize}
}
{
    \end{itemize}
    \end{minipage}
}

\heading{Projects}

\begin{project}{This Resume}{February 2022 - Present}
    \item I didn’t have Microsoft Word anymore, so I wrote this in YAML and rendered it into the document you are reading. :-)
\end{project}

\begin{project}{Capstone Research}{Fall 2019 -- Spring 2020}
    \item Developed an "automated advising assistant" (Django/React app) to help UVA students create a long-term course plan based on a weighted scheduling algorithm. Worked on the Full-Stack/Application Team, and personally played a key role in integrating the code between teams.
\end{project}

\begin{project}{TA sorter}{Spring 2019}
    \item Created a quick program to help us sort out TA office hours and lab preferences using Max Flow.
\end{project}

\begin{project}{Yelp for Off-Grounds Housing}{Spring 2019}
    \item Worked on a SCRUM team to create a Django app to help students browse housing in Charlottesville.
\end{project}

\begin{project}{Office Hours Chrome Extension}{Fall 2018}
    \item Created a Chrome extension to notify TAs when a student needs help in Office Hours.
\end{project}

\end{document}